---
output:
  word_document: default
  html_document: default
---
```{r}
# setwd('desktop')
df = read.csv('heli.csv')
df$Treef = as.factor(df$Tree)
```

```{r}
#a)
plot(df$Load, df$Velocity, pch = array(df$Treef), col = df$Tree+1)
```
From the plot, there looks to be a strong positive linear relationship between Load and Velocity. However, heterosexuality may need to be monitored.


```{r}
#b)
addModel = lm(Velocity ~ Load + Treef, data = df)
intModel = lm(Velocity ~ Load * Treef, data = df)
anova(addModel, intModel)
```
P-value of 0.05011 is very close to significance of 0.05. Should collect more data and retest. Otherwise, P-value < 0.1 is also commonly used for significance of interaction, and denotes 'somewhat significant'; so in this case the interaction model should be kept based on the result of this test.


```{r}
#c) 
model = lm(Velocity~Load*Treef, data = df)
drop1(model, scope = ~., test = "F")
# puts "None" as top pick because the interaction term is < 0.1 - moderate significance; but Tree itself has p value > 0.05 so both should be removed

model2 = lm(Velocity~Load, data = df)
drop1(model2, scope = ~., test = "F")

summary(model2)
```
The final model is Velocity = -0.09326 + 5.82019*Load


```{r}
#d)

plot(df$Load, df$Velocity) 

abline(coef = c(model2$coefficients[1], model2$coefficients[2]))

```

```{r}
plot(df$Load, df$Velocity, pch = array(df$Treef), col = df$Tree+1)

abline(coef = c(intModel$coefficients[1], intModel$coefficients[2]), col = 'red')

abline(coef = c(intModel$coefficients[1]+intModel$coefficients[3], intModel$coefficients[2]+intModel$coefficients[5]), col = 'green')

abline(coef = c(intModel$coefficients[1]+intModel$coefficients[4], intModel$coefficients[2]+intModel$coefficients[6]), col = 'blue')
```


```{r}
#e)
library(car)
dst = matrix(c(1), 1, 1)
C = matrix(c(1, 0.2, 1, 0, 0.2, 0), 1, 6, byrow = T)
linearHypothesis(intModel, C, dst)

```
Since P value = 0.04219 < 0.05, there is sufficient evidence to reject the null hypothesis that Samara from tree 2 with disk loading of 0.2 has avg descent velocity of 1.